### 2021-08-12 README.Rmd
Update readme

<!-- badges: start -->
<!-- [![Codecov test coverage](https://codecov.io/gh/zonebuilders/zonebuilder/branch/master/graph/badge.svg)](https://codecov.io/gh/zonebuilders/zonebuilder?branch=master) -->
<!-- [![R-CMD-check](https://github.com/zonebuilders/zonebuilder/workflows/R-CMD-check/badge.svg)](https://github.com/zonebuilders/zonebuilder/actions) -->
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/zonebuilder)](https://CRAN.R-project.org/package=zonebuilder) -->
<!-- badges: end -->

>>>>

<!-- badges: start -->
<!-- [![Codecov test coverage](https://codecov.io/gh/zonebuilders/zonebuilder/branch/master/graph/badge.svg)](https://codecov.io/gh/zonebuilders/zonebuilder?branch=master) -->
[![R-CMD-check](https://github.com/zonebuilders/zonebuilder/workflows/R-CMD-check/badge.svg)](https://github.com/zonebuilders/zonebuilder/actions)
[![CRAN status](https://www.r-pkg.org/badges/version/zonebuilder)](https://CRAN.R-project.org/package=zonebuilder)
[![CRAN RStudio mirror
downloads](https://cranlogs.r-pkg.org/badges/grand-total/zonebuilder)](https://www.r-pkg.org/pkg/zonebuilder)
[DOI](https://doi.org/10.31219/osf.io/vncgw)
<!-- badges: end -->
